\section{Discussion}
\label{sec:discussion}

The precise replication of the 3Q $\to$ 5Q $\to$ 4Q transition sequence demonstrates the robustness of the exact steepest descent method when coupled with strategic optimization techniques. Our results show that the critical mixing ratios $p_{c1} \approx 0.512$ and $p_{c2} \approx 0.527$ are recovered with high accuracy, matching the benchmarks of the original study \cite{Kato2023} within 1\% tolerance. This level of agreement confirms that the variational functional $G$ correctly captures the thermodynamic limit of the partition function for these complex topological states.

A key insight from our implementation is the critical role of the energy landscape's topology. The 5Q state, while being the global minimum in the intermediate $p$-regime, resides in a narrow basin of attraction. Standard random initialization often fails to locate this state, instead stalling in the 3Q or 4Q local minima. The success of the \textbf{Guided Seed Injection} strategy suggests that the 5Q state is not a completely isolated island in configuration space, but is reachable if the optimizer is initialized in the proximity of the underlying 3Q or 1Q symmetries. This implies that the 5Q phase emerges as a structured deformation of simpler multi-Q states rather than a stochastic fluke.

Furthermore, the verification of "hidden" transitions provides a profound illustration of the distinction between thermodynamic and topological phase transitions. The fact that the monopole density $N_m$ and scalar chirality $\chi_{sc}$ exhibit sharp discontinuities while the specific heat $C$ remains smooth indicates that the transition is driven by a global reconfiguration of the spin field that does not entail a significant change in the internal energy's temperature derivative. Such transitions are indicative of a topological reorganization of the ground state that is decoupled from the system's thermal fluctuations.

The JAX-accelerated framework developed here allows for rapid exploration of the $p-h-T$ parameter space, which was previously computationally prohibitive. The ability to perform parallel seed sampling via \texttt{jax.pmap} and ensure reproducibility through deterministic hashing provides a scalable path toward studying other emergent monopole lattices in different geometries or with additional interactions, such as anisotropic exchange or spin-orbit coupling.
