\section{Introduction}
\label{sec:intro}

The study of emergent topological excitations in magnetic systems has revealed a diverse array of phases, among which the magnetic monopole lattice stands as a particularly intriguing example. In certain frustrated spin systems, the competition between multiple exchange interactions can lead to the formation of complex multi-Q states, where the magnetic order is characterized by the superposition of several spin-density waves. A striking feature of such systems is the emergence of magnetic monopoles—singularities in the magnetization field—which organize into regular lattices.

Recent theoretical work has proposed the existence of "hidden" topological transitions in these lattices, where the monopole density $N_m$ changes abruptly without the accompanying thermodynamic singularities typically expected at a phase transition. Specifically, in the study of emergent monopole lattices described by Kato and Motome \cite{Kato2023}, it was found that transitions between 3Q, 5Q, and 4Q states occur as a function of the mixing ratio $p$ between different interaction regimes. These transitions are characterized by a change in the topological charge of the lattice but remain invisible to the specific heat $C$, making them "hidden" from standard thermodynamic probes.

However, the numerical identification of these states is notoriously difficult. The variational energy landscape of the multi-Q states is highly rugged, with numerous local minima that can trap standard optimization algorithms, leading to an incorrect identification of the ground state or a failure to resolve the 5Q intermediate phase.

In this work, we present a strict numerical replication of these hidden topological transitions. We employ the exact steepest descent method, implemented via a JAX-accelerated framework, to find the global maximum of the variational free energy functional $G$. To overcome the challenge of the rugged energy landscape, we introduce a guided seed injection strategy and a simulated annealing schedule. We demonstrate that our approach precisely reproduces the 3Q $\to$ 5Q $\to$ 4Q ground state sequence and the critical mixing ratios $p_{c1} \approx 0.512$ and $p_{c2} \approx 0.527$. By analyzing the scalar spin chirality and the specific heat, we provide a clear verification of the hidden nature of these topological transitions, thereby validating the efficacy of the exact steepest descent method for the study of complex topological spin lattices.
