\section{Computational Method}
\label{sec:method}

To solve the variational problem of maximizing $G(\{\mathbf{S}_0\})$, we implemented a high-performance computational engine using the JAX framework and the Optax optimization library. The optimization is performed over the spin angles $\{\theta_i, \phi_i\}$ and the local field parameters $\{v_i\}$ for all $N$ sites in the magnetic unit cell.

To navigate the rugged energy landscape of the 5Q state, which is prone to numerous local minima, we employ a multi-tiered optimization strategy. First, we utilize \texttt{jax.pmap} to execute parallel searches across multiple GPU devices. For each point in the parameter space, we initialize a batch of random seeds. To ensure that the global minimum is not missed, we supplement these random starts with \textbf{Guided Seed Injection}. Specifically, we inject physically motivated initial configurations, including a field-aligned 1Q spiral and a pristine 3Q skyrmion state rotated to align with the applied external field $\mathbf{h}$.

The optimization process incorporates a linear simulated annealing schedule. The temperature $T$ is gradually lowered from a starting value $T_{\text{start}} \approx T + 0.5$ to the target temperature, with the optimizer state reset at each temperature step to prevent momentum-induced instability. We use the Adam optimizer with an exponentially decaying learning rate to refine the final configuration.

To accurately compute thermodynamic derivatives, such as the specific heat $C = \partial E / \partial T$, we implement a \textbf{Dual-Search strategy}. This approach combines a global random search with a local phase tracker. The local tracker uses the optimized state from the previous temperature step as a seed, ensuring that the system evolves adiabatically. To prevent discontinuous jumps in the topological charge $N_m$ during the derivative calculation, we employ a basin-safe logic: if a step in $T$ triggers a change in $N_m$, the energy difference is calculated using only the state that preserves the current topological sector.

For exact reproducibility, the random seed for each simulation is generated via an MD5 hash of the parameters $(p, h, T)$, ensuring that the optimization trajectory is deterministic across different compute nodes.
